---
title: "Waabanong Weekly Iteration Update"
date: today
client: "PCFS"
docket: "PD25-1186-CO"
format:
  docx:
    reference-doc: _templates/report-template.docx
    toc: false
    number-sections: false
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(lubridate)
library(scales)

plan  <- read.csv("data/iteration_plan.csv",  stringsAsFactors = FALSE)
tasks <- read.csv("data/iteration_tasks.csv", stringsAsFactors = FALSE)

plan <- plan |>
  mutate(
    start_date      = as.Date(start_date),
    end_date        = as.Date(end_date),
    status          = factor(status,
                             levels = c("Complete", "Development", "in Design",
                                        "Planning", "Planned")),
    subtask_label   = factor(subtask_label, levels = c("UAT", "Dev")),
    iteration_label = paste0("Iteration ", iteration, "\n", iteration_name),
    fill_key        = paste0(subtask_type, "_", as.character(status))
  )

iter_label_levels <- plan |>
  distinct(iteration, iteration_label) |>
  arrange(iteration) |>
  pull(iteration_label)

plan <- plan |>
  mutate(iteration_label = factor(iteration_label, levels = iter_label_levels))
```

# Iteration Plan

```{r progress-summary, echo=FALSE, results='asis'}
today       <- Sys.Date()
target_date <- as.Date("2026-06-05")
days_left   <- as.integer(target_date - today)

status_counts <- plan |>
  filter(subtask_type == "dev") |>
  count(status) |>
  mutate(status = as.character(status))

get_n <- function(s) {
  val <- status_counts$n[status_counts$status == s]
  if (length(val) == 0) 0L else val
}

n_complete <- get_n("Complete")
n_dev      <- get_n("Development")
n_design   <- get_n("in Design")
n_planned  <- get_n("Planned")
n_total    <- nrow(plan |> filter(subtask_type == "dev"))

# Latest end date among active (Development / in Design) iterations
active_rows <- plan |>
  filter(subtask_type == "dev",
         status %in% c("Development", "in Design"))
latest_active_end <- if (nrow(active_rows) > 0) max(active_rows$end_date) else today

# Projected last dev end date
projected_end <- max(plan$end_date[plan$subtask_type == "dev"])
on_track <- projected_end <= target_date

track_word  <- if (on_track) "**On Track**" else "**At Risk**"
track_color <- if (on_track) "276749" else "991B1B"
track_tag   <- paste0(
  '`<w:r><w:rPr><w:color w:val="', track_color, '"/><w:b/></w:rPr>',
  '<w:t>', if (on_track) "\u2714 On Track" else "\u26A0 At Risk",
  '</w:t></w:r>`{=openxml}'
)

cat(paste0(
  "> **Week of ", format(today, "%B %d, %Y"), "** \u2014 ",
  track_tag, "  \n",
  "> ", n_complete, " of ", n_total, " iterations complete. ",
  if (n_dev > 0)    paste0(n_dev,    " in active development. ") else "",
  if (n_design > 0) paste0(n_design, " in design. ")             else "",
  if (n_planned > 0) paste0(n_planned, " planned.  \n") else "\n",
  "> Target completion: **", format(target_date, "%B %d, %Y"),
  "** (", days_left, " days). Projected finish: **",
  format(projected_end, "%B %d, %Y"), "**."
), "\n\n")
```

> Data Cleaning & Migration (Iteration 6) runs independently Apr 14 – May 5 under a separate team. Dates are subject to revision following the re-baselined project timeline (A-112).

## Schedule

```{r gantt, echo=FALSE, fig.width=9, fig.height=8, dpi=150}
gantt_plan  <- plan |> filter(iteration != 1)
x_min       <- min(gantt_plan$start_date) - 3
x_max       <- max(gantt_plan$end_date)   + 3

fill_values <- c(
  "dev_Development" = "#1B4F8A",   # deep navy      — Dev: in development
  "dev_in Design"   = "#6D28D9",   # deep purple    — Dev: in design
  "dev_Planning"    = "#0369A1",   # dark sky-blue  — Dev: planning
  "dev_Planned"     = "#60A5FA",   # sky blue       — Dev: planned
  "dev_Complete"    = "#6B7280",   # gray           — Dev: complete
  "uat_Development" = "#B45309",   # deep amber     — UAT: in development
  "uat_in Design"   = "#D97706",   # mid amber      — UAT: in design
  "uat_Planning"    = "#0E7490",   # dark cyan      — UAT: planning
  "uat_Planned"     = "#FCD68A",   # pale amber     — UAT: planned
  "uat_Complete"    = "#9CA3AF"    # light grey     — UAT: complete
)

legend_labels <- c(
  "dev_Development" = "Dev \u2014 Development",
  "dev_in Design"   = "Dev \u2014 In Design",
  "dev_Planning"    = "Dev \u2014 Planning",
  "dev_Planned"     = "Dev \u2014 Planned",
  "dev_Complete"    = "Dev \u2014 Complete",
  "uat_Development" = "UAT \u2014 Development",
  "uat_in Design"   = "UAT \u2014 In Design",
  "uat_Planning"    = "UAT \u2014 Planning",
  "uat_Planned"     = "UAT \u2014 Planned",
  "uat_Complete"    = "UAT \u2014 Complete"
)

legend_order <- c("dev_Development", "dev_in Design", "dev_Planning", "dev_Planned", "dev_Complete",
                  "uat_Development", "uat_in Design", "uat_Planning", "uat_Planned", "uat_Complete")

ggplot(gantt_plan) +
  geom_rect(
    aes(
      xmin = start_date,
      xmax = end_date,
      ymin = as.numeric(subtask_label) - 0.38,
      ymax = as.numeric(subtask_label) + 0.38,
      fill = fill_key
    ),
    color = "white",
    linewidth = 0.3
  ) +
  facet_grid(iteration_label ~ ., switch = "y") +
  scale_fill_manual(
    values = fill_values,
    labels = legend_labels,
    breaks = legend_order,
    drop   = FALSE
  ) +
  scale_x_date(
    limits      = c(x_min, x_max),
    date_breaks = "1 week",
    date_labels = "%b %d",
    expand      = expansion(add = 0)
  ) +
  scale_y_continuous(
    breaks = c(1, 2),
    labels = c("UAT", "Design & Dev"),
    expand = expansion(add = 0.5)
  ) +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme_minimal(base_size = 14) +
  theme(
    strip.placement      = "outside",
    strip.text.y.left    = element_text(angle = 0, hjust = 1,
                                        size = 11, face = "bold",
                                        lineheight = 1.15,
                                        margin = margin(r = 8)),
    panel.grid.major.y   = element_blank(),
    panel.grid.minor     = element_blank(),
    panel.grid.major.x   = element_line(color = "#E5E7EB", linewidth = 0.3),
    panel.spacing        = unit(0.2, "lines"),
    panel.background     = element_rect(fill = "#FAFAFA", color = NA),
    strip.background     = element_rect(fill = "#F3F4F6", color = NA),
    axis.text.y          = element_text(size = 12, color = "#374151"),
    axis.text.x          = element_text(size = 10, angle = 45, hjust = 1),
    legend.position      = "bottom",
    legend.key.size      = unit(0.6, "cm"),
    legend.text          = element_text(size = 12),
    legend.spacing.x     = unit(0.45, "cm")
  )
```

## Meetings

| # | Meeting | Date |
|---|---------|------|
| M-01 | PCFS In-Person Meeting | April 13, 2026 |
| M-02 | PCFS In-Person Meeting | May 5, 2026 |
| M-03 | PCFS In-Person Meeting | May 19, 2026 |
| M-04 | PCFS In-Person Meeting | June 2, 2026 |
| M-05 | PCFS In-Person Meeting | June 15, 2026 |

## Iteration Scope

```{r active-tasks, echo=FALSE, results='asis'}
# Hex colours matched exactly to Gantt dev bar fill_values
status_hex <- c(
  "Development" = "1B4F8A",
  "in Design"   = "6D28D9",
  "Planning"    = "0369A1",
  "Planned"     = "60A5FA",
  "Complete"    = "6B7280"
)

make_tag <- function(label, hex) {
  paste0(
    '`<w:r><w:rPr><w:color w:val="', hex, '"/><w:b/></w:rPr>',
    '<w:t xml:space="preserve">[', label, '] </w:t></w:r>`{=openxml}'
  )
}

active_subtasks <- plan |>
  filter(subtask_type == "dev") |>
  arrange(iteration)

for (i in seq_len(nrow(active_subtasks))) {
  row    <- active_subtasks[i, ]
  status <- as.character(row$status)
  hex    <- status_hex[status]
  tag    <- make_tag(status, hex)
  dates  <- paste0(format(row$start_date, "%b %d"),
                   " \u2013 ",
                   format(row$end_date, "%b %d, %Y"))

  heading <- paste0(
    "### ", tag,
    "Iteration ", row$iteration, " \u2014 ", row$iteration_name,
    " (", dates, ")"
  )
  cat(heading, "\n\n")

  iter_tasks <- tasks |>
    filter(iteration == row$iteration, subtask_type == row$subtask_type) |>
    arrange(task_order)

  if (nrow(iter_tasks) > 0) {
    for (j in seq_len(nrow(iter_tasks))) {
      cat("-", iter_tasks$task_description[j], "\n")
    }
  } else {
    cat("_No tasks recorded for this subtask._\n")
  }
  cat("\n")
}
```

## Outstanding Questions

| # | Question |
|---|----------|
| Q-01 | What exact Sage 300 version and build is in use? Required to finalize integration design scope. |
| Q-02 | What are the complete requirements for role-based access, high-profile cases, and conflict-of-interest restrictions? |
| Q-03 | What agency email account will be used for external notification sends (Microsoft REST API)? |
| Q-04 | What additional requirements does the after-hours team have for address-based search? |
| Q-05 | What finance requirements emerge from CFO / Director of Finance engagement beginning April 7th? |
| Q-06 | Is it possible to have two intakes open simultaneously? |
| Q-07 | What is an assessment worker exactly, and how is a given intake assigned to a specific worker? |
| Q-08 | Can a data entry worker start or edit Intakes, or only verify them and enter into CFSIS? How is the work currently distributed? |
| Q-09 | Who can submit a finance sheet — only supervisors? What is the complete list of finance sheet request types we need to support? |
